Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-15 paper/abstraction/appendix.tex
minor edits

\emph{Case $l$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(l,\Gamma,f)) &\iff& f(p) \in \Lang(l) \\
    p \in \Lang(\Sigma_i ~ f_i^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
    p \in \bigcup_i f_i^{-1}(l) &\iff& f(p) \in \Lang(l) \\
    p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
    p \in f^{-1}(l) &\iff& f(p) = l \\
    \text{by the homomorphism} & & \\
  \end{array} \]

@@

  Now we prove that $f_{pg}: G' \rightarrow G'^A$ is a valid homomorphism
  \begin{proof}
    From Lemma 5, $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$. 
    %
    Assume there is an edge in $PG$ from $x=(l,q_1,\ldots,q_n)$
    to $y=(l',q_1',\ldots,q_n')$. We know that $f(x) = (f(l),q_1,\ldots,q_n)$ and $f(y) = (f(l'),q_1',\ldots,q_n')$.
    %
    From the construction of PG, we know that $\sigma_i(q_k, l) = q_k'$. 
    Also from the construction of the abstract automata, we also know that $\sigma_i(q_k, l) = q_k' \iff \sigma^A_i(q_k, f(l)) = q_k'$. Therefore, we can conclude that $\sigma^A_i(q_k, f(l)) = q_k'$. However, from the definition of $PG^A$, this means that there must be an edge in $PG^A$ for ($f(x),f(y)$).
  \end{proof}
\end{lem}

@@

\vspace{1em}
\begin{lem}
  For all node $m$, $\Pref(m) = \Pref^A(f_{pg}(m))$.
  \begin{proof}
    $\Pref$ and $\Pref^A$ assign values to PG nodes for each topology location as increasing integers starting from 0 according to the total ordering for $\leq$.
    From Lemma 10, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$. Also, because there can only be a single product graph node for a particular location and set of states (since automata are determinized), and from Lemma 5 we know that for each $m$ there exists a node $f(m)$ with the same states it must be the case that $\Pref(m) = \Pref^A(f_{pg}(m))$
  \end{proof}
\end{lem}

@@

    \vspace{1em}
    \noindent
    Now suppose the other direction. There is an element $x \in \{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \mathrm{adjIn}(PG^A,f_{pg}(m)) \}$. We know that $f(x) = B$, and that there is a topology edge between $b$ and $\ell$. Lemma 7 together with the fact that $f(\ell) = \Topo(m)$ lets us conclude that there is an edge in the concrete $PG$ between $(b,q_N)$ and $m$. It follows then that $x \in \{ b ~\vert~ (b,q_N) \in \mathrm{adjIn}(PG,m)\}$.

>>>>

\emph{Case $l$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(l,\Gamma,f)) &\iff& f(p) \in \Lang(l) \\
    p \in \Lang(\Sigma ~ f^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
    p \in \bigcup f^{-1}(l) &\iff& f(p) \in \Lang(l) \\
    p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
    p \in f^{-1}(l) &\iff& f(p) = l \\
    \text{by the homomorphism} & & \\
  \end{array} \]

@@

  Now we prove that $f_{pg}: G' \rightarrow G'^A$ is a valid homomorphism
  \begin{proof}
    From Lemma 5, $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$. 
    %
    Assume there is an edge in $PG$ from $x=(l,q_1,\ldots,q_n)$
    to $y=(l',q_1',\ldots,q_n')$. We know that $f(x) = (f(l),q_1,\ldots,q_n)$ and $f(y) = (f(l'),q_1',\ldots,q_n')$.
    %
    From the construction of PG, we know that $\sigma_i(q_k, l) = q_k'$. 
    Also from the construction of the abstract automata, we also know that $\sigma_i(q_k, l) = q_k' \iff \sigma^A_i(q_k, f(l)) = q_k'$. Therefore, we can conclude that $\sigma^A_i(q_k, f(l)) = q_k'$. From the definition of $PG^A$, this means that there must be an edge in $PG^A$ for ($f(x),f(y)$).
  \end{proof}
\end{lem}

@@

\vspace{1em}
\begin{lem}
  For all nodes $m$, $\Pref(m) = \Pref^A(f_{pg}(m))$.
  \begin{proof}
    $\Pref$ and $\Pref^A$ assign values to PG nodes for each topology location as increasing integers starting from 0 according to the total ordering for $\leq$.
    From Lemma 10, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$. Also, because there can only be a single product graph node for a particular location and set of states (since automata are determinized), and from Lemma 5 we know that for each $m$ there exists a node $f(m)$ with the same states it must be the case that $\Pref(m) = \Pref^A(f_{pg}(m))$
  \end{proof}
\end{lem}

@@

    \vspace{1em}
    \noindent
    Now suppose the other direction. There is an element $x \in \{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \mathrm{adjIn}(PG^A,f_{pg}(m)) \}$. We know that $f(x) = B$, and that there is a topology edge between $b$ and $\ell$. Lemma 8 together with the fact that $f(\ell) = \Topo(m)$ lets us conclude that there is an edge in $PG$ between $(b,q_N)$ and $m$. It follows then that $x \in \{ b ~\vert~ (b,q_N) \in \mathrm{adjIn}(PG,m)\}$.
